---
title: "Project Report"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: "hide"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

library(tidyverse)
library(leaflet)
library(ggplot2)
library(plotly)
library(ggwordcloud)
library(performance)
library(ggpubr)
library(knitr)
library(maps)
library(forcats)

cleaned_df<-
  read_csv("Data/cleaned_youtube_df.csv")|>
  janitor::clean_names() |>
  filter(created_year >= 2005)
```

## Motivation

In contemporary times, social media has assumed a multifaceted role. Individuals utilize platforms like YouTube not only for educational purposes but also for listening to music and staying informed with current news. This versatility makes YouTube a crucial player in shaping digital culture and trends. Consequently, understanding the factors that lead to a YouTuber's success is vital, as it influences not only individual creators but also the broader media landscape. By analyzing data from top YouTubers across various countries, the project aims to provide valuable insights for content creators and advertisers to enhance their engagement and profitability. The primary dataset obtained from [Kaggle](https://www.kaggle.com/datasets/nelgiriyewithana/global-youtube-statistics-2023) comprises information from the top 995-ranked YouTubers in the global YouTube community. We utilize advanced data visualization techniques to deeply analyze top YouTubers' profiles, examining their demographic distribution and the relationships among various success-related variables. Moreover, our project includes the development of a predictive model designed to quantify and forecast YouTubers' success, offering valuable insights into the future trends of content creation and audience engagement on the platform.

## Related work

Park M et al.'s 2017 study (Cultural values and cross-cultural video consumption on YouTube) delves into the consumption patterns of popular YouTube videos across countries, taking into account differences in cultural values, language, GDP, and internet penetration. Additionally, the 2016 study by Welbourne, D. J., and Grant, W. J. study the elements that influence the popularity of Science communication videos on YouTube, and find out that while professional content is more abundant, user-generated content tends to be more popular with audiences. Also one user from [reddit](https://www.reddit.com/r/youtube/comments/15a1vi0/differences_in_the_content_experience_in/?rdt=42149) raised a similar question about his channels, which feature similar content but exhibit a significant disparity in subscriber numbers between the English and Ukrainian versions. These studies and observations inspire our project to further explore the intricate factors influencing YouTube channel success, emphasizing the geographical and content factors.


## Initial questions

- 1.Define what "success" means in the context of a YouTuber.
- 2.What are the factors that influence the success of YouTubers?
- 3.Develop a predictive model to forecast YouTubers' success.
  
## Data Cleaning and Preprocessing

We imported the data and apply the function `janitor::clean_names` to convert all the variable names to lower case and puts underscores in the gaps. Since YouTube was created in 2005, we eliminated 6 accounts created before 2005, which might be data entry error. The 'country' and 'category' variables have been encoded as factors to facilitate categorical analysis. We also add two new variables 'video_per_upload' and 'earning_differences'. For the consideration of data integrity, `NA` are kept for not a  significant reduction in dataset size, and we will process the NA values respecively in each visualization and model fitting. The cleaned dataset comprises 588 observations across 20 variables which are integral for our exploratory data analysis and model fitting processes:

- `id`
- `subscribers`: Number of subscribers to the channel
- `video views`: Total views across all videos on the channel
- `category`: Category or niche of the channel
- `uploads`: Total number of videos uploaded on the channel
- `country`: Country where the YouTube channel originates
- `channel_type`: Type of the YouTube channel (e.g., individual, brand)
- `video_views_rank`: Ranking of the channel based on total video views
- `country_rank`: Ranking of the channel based on the number of subscribers within its country
- `channel_type_rank`: Ranking of the channel based on its type (individual or brand)
- `video_views_for_the_last_30_days`: Total video views in the last 30 days
- `lowest_monthly_earnings`: Lowest estimated monthly earnings from the channel
- `highest_monthly_earnings`: Highest estimated monthly earnings from the channel
- `lowest_yearly_earnings`: Lowest estimated yearly earnings from the channel
- `highest_yearly_earnings`: Highest estimated yearly earnings from the channel
- `subscribers_for_last_30_days`: Number of new subscribers gained in the last 30 days
- `created_year`: Year when the YouTube channel was created
- `Population`: Total population of the country
- `latitude`: Latitude coordinate of the country's location
- `longitude`: Longitude coordinate of the country's location
- `video_per_upload`: Average number of video views per video upload
- `earning_differences`: Range of yearly earnings for each channel, calculated by subtracting `lowest_yearly_earnings` from `highest_yearly_earnings`.

```{r}
# Make sure 'country' and 'category' are factors.
cleaned_df$country <- as.factor(cleaned_df$country)
cleaned_df$category <- as.factor(cleaned_df$category)

# Add new variables 'video_per_upload' and 'earning_differences'
cleaned_df$video_per_upload <- with(cleaned_df, video_views / uploads)
cleaned_df$earning_differences <- with(cleaned_df, highest_yearly_earnings - lowest_yearly_earnings)
```


In order to preserve data integrity and avoid a significant reduction in dataset size, we have opted to retain `NA` values within the dataset. Each instance of `NA` will be addressed individually in subsequent stages of our analysis, ensuring that they are appropriately managed during both the visualization and model fitting processes. 


## EDA

### 1. Univariate Analysis


#### How are the distribution of numerical variables?

```{r fig.width = 9,fig.asp = 1.2,out.width = "100%"}
youtube_df <- cleaned_df

all_columns <- colnames(youtube_df)
columns_to_plot <- all_columns[!all_columns %in% c("id", "category","country","abbreviation","channel_type","population","latitude","longitude","created_year")]


numeric_data_long <- 
  youtube_df[, columns_to_plot] %>% 
  gather(key = "variable", value = "value")


# Create a single plot with facets for each numeric variable
p <- ggplot(numeric_data_long, aes(x = value)) +
  geom_histogram(aes(y = ..density..),bins = 15, fill = "#8dab7f", alpha = 0.8) +
  geom_density(color="#6b8e23")+
  facet_wrap(~ variable, scales = "free", ncol = 3) +
  scale_x_continuous(labels = scales::comma) +
  theme_minimal(base_size = 10) +  
  theme(
    strip.text.x = element_text(size = 10, face = "bold"), 
    axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1,size=7,face = "bold"), # Angle x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    plot.margin = margin(1, 1, 1, 1, "cm"), # Adjust the plot margins
    strip.background = element_blank(),
    panel.spacing = unit(3, "lines")
  ) +
  labs(
    title = "Distribution of Numeric Variables",
    x = "Value",
    y = "Frequency",
    caption = "Source: YouTube Data"
  )
# Convert to an interactive plot
ggplotly(p)
```

We create interactive plots by applying `ploty` to visualize the density distribution of numerical variables. Upon observing right skewness, we apply a logarithmic transformation to these numeric values. 

```{r fig.width = 9,fig.asp = 1.2,out.width = "100%"}
p <- ggplot(numeric_data_long, aes(x = log(value+1))) +
  geom_histogram(aes(y = ..density..),bins = 15, fill = "#8dab7f", alpha = 0.8) +
  geom_density(color="#6b8e23")+
  facet_wrap(~ variable, scales = "free", ncol = 3) +
  scale_x_continuous(labels = scales::comma) +
  theme_minimal(base_size = 10) +  
  theme(
    strip.text.x = element_text(size = 10, face = "bold"), 
    axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1,size=7,face = "bold"), # Angle x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    plot.margin = margin(1, 1, 1, 1, "cm"), # Adjust the plot margins
    strip.background = element_blank(),
    panel.spacing = unit(3, "lines")
  ) +
  labs(
    title = "Distribution of Numeric Variables",
    x = "Value",
    y = "Frequency",
    caption = "Source: YouTube Data"
  )
# Convert to an interactive plot
ggplotly(p)
```



#### Channel created year summary

```{r}
year_created_plot <- plot_ly(cleaned_df, x = ~created_year, type = "histogram", 
                marker = list(color = "#B3CDD1", line = list(color = "white", width = 1)),
                nbinsx = 30)

# Update layout
year_created_plot <- year_created_plot |>
  layout(
    title = "Distribution of Channel Creation Years",
    xaxis = list(title = "Year of Creation"),
    yaxis = list(title = "Number of Channels"),
    showlegend = FALSE,
    template = "plotly_white"  # Optional: Set a template for the plot
  )


year_created_plot
```


There is an initial growth in the number of channels created from 2005 onwards, which is expected as YouTube was founded in February 2005 and gradually gained popularity.

A peak in channel creation appears to occur in the early 2010s, which may correspond with YouTube's rise in global accessibility and the platform becoming a viable career option for content creators.

Post-2015, there's a noticeable decline in new channel creation. This could be due to market saturation or content creators choosing to diversify onto emerging platforms.


#### Word Cloud


```{r}
category_data <- youtube_df %>%
  filter(!is.na(category) & category != "nan") %>%
  count(category) %>%
  mutate(n=n*30) %>% 
  ungroup()


category_data$scaled_size <- log(category_data$n + 1) # adding 1 to avoid log(0)

wordcloud_plot <- ggplot(category_data, aes(label = category, size = scaled_size)) +
  geom_text_wordcloud(
    aes(color = n),
    shape = 'circle',
    rm_outside = TRUE
  ) +
  scale_size_area(max_size = 10) + 
  scale_color_gradient(low = "#ffcc99", high = "#8dab7f") +
  theme_void(base_family = "sans") +
  theme(legend.position = "none", 
        plot.margin = margin(1, 1, 1, 1, "cm")) # Adjust margins around the plot

# Display the plot
wordcloud_plot

```

We exclude the NaN values in the category, and modify the frequency `n` of each category. 
The most frequently used categories, as observed from the word cloud chart, include `Entertainment`, `Music`, `People & Blogs`, and `Gaming`.


#### Pie Chart

```{r}
channel_type_counts <- table(youtube_df$channel_type)

channel_type_counts <- youtube_df %>%
  group_by(channel_type) %>%
  summarise(count = n()) %>%
  ungroup()

color <- c("#ffcc99","#ffe4b5", "#ffd180","#ffa07a","#d1d17a", "#8dab7f", "#D2DFD9", "#A8C0B5", "#D1B9CB", "#B3CDD1", "#BBC1D0", "#E8C3C3","#C7CEBD", "#D2DFD9","#6b8e23")

# Create a pie chart using plotly with the custom colors
fig <- plot_ly(channel_type_counts, labels = ~channel_type, values = ~count, type = 'pie',
               textinfo = 'label+percent',
               insidetextorientation = 'radial',
               marker = list(colors = color))
fig %>% 
  layout(title = 'Pie Chart of Channel Types',
         showlegend = FALSE,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

```

In this interactive pie chart, we demonstrate the frequency of proportion in Channel type. The most frequently viewed channel, as observed from the word cloud chart, include `Entertainment`, `Music`, `People & Blogs`, `Gaming` and `Comedy`.


### 2. Multivariate Analysis

#### Mean and median earning differences by YouTube content category
```{r}
summary_data <- cleaned_df |>
  mutate(earning_diff = highest_yearly_earnings - lowest_yearly_earnings)|>
  filter(category != "nan")|>
  group_by(category) |>
  summarize(mean_earning_diff = mean(earning_diff),
            median_earning_diff = median(earning_diff),)

# Create a bar plot using Plotly
plot <- plot_ly(data = summary_data, x = ~category, type = 'bar',
                y = ~mean_earning_diff, name = 'Mean Earning Difference',marker = list(color = "#F4E1C1")) %>%
  add_trace(y = ~median_earning_diff, name = 'Median Earning Difference', marker = list(color = "#C7CEBD"))

# Add layout details
plot <- plot|>
  layout(title = 'Earning Difference Summary by Category',
               xaxis = list(title = 'Category'),
               yaxis = list(title = 'Earning Difference'),
         legend = list(orientation = 'h', x = 0.5, y = -0.3, xanchor = 'center', yanchor = 'top'))

# Show the plot
plotly::layout(plot, layout)
```
For most categories, the mean earning difference is higher than the median, suggesting that a few channels with substantially higher earnings may be skewing the mean upwards. 

#### Top 15 YouTube Channels by Highest Yearly Earnings
```{r}
color <- c("#ffe4b5", "#ffa07a","#d1d17a" , "#D2DFD9", "#A8C0B5", "#D1B9CB", "#B3CDD1", "#BBC1D0", "#E8C3C3")

earning_plot_data <-
  read_csv("Data/Global YouTube Statistics.csv",locale = locale(encoding = "Windows-1252"))  %>%
  janitor::clean_names() %>% 
  drop_na() %>% 
  select(youtuber, channel_type, highest_yearly_earnings) %>% 
  mutate(youtuber = stringi::stri_replace_all_regex(youtuber, "[^\x01-\x7F]", "")) %>% 
  arrange(desc(highest_yearly_earnings)) %>%
  top_n(15, highest_yearly_earnings)



plot_ly(earning_plot_data, x = ~highest_yearly_earnings, y = ~youtuber, 
                type = 'bar', orientation = 'h',
                color = ~channel_type, colors = color,
                text = ~paste('$', formatC(highest_yearly_earnings, format = "d", big.mark = ",")),
                textposition = 'inside',
                insidetextanchor = 'end', 
                textfont = list(color = 'white'), # text color
                hoverinfo = 'text',
                hovertemplate = paste('<b>Youtuber:</b> %{y}<br>',
                                      '<b>Earnings:</b> $%{x}<extra></extra>')) %>%
  layout(title = 'Top 15 YouTube Channels by Highest Yearly Earnings',
         xaxis = list(title = 'Yearly Earnings ($)'),
         yaxis = list(title = ''),
         showlegend = TRUE,
         margin = list(l = 100, r = 25, t = 50, b = 50),
         font = list(family = "Arial, sans-serif", size = 12, color = "#333333"))

```
For the Top 15 YouTube Channels by Highest Yearly Earnings, first and foremost, KIMPO has the highest earnings at 163,400,400 US dollars in 2023, which is triple of the lowest earnings(59,800,000 dollars) of dednahype. Secondly, Entertainment is still the most predominant category among these channels. In the 15 YouTube Channels, animal and comedy have respectably only one position.

#### How does the top youtubers spread over countries?
```{r}
channel_counts_by_location <- cleaned_df|>
  drop_na(c(latitude, longitude)) |>
  group_by(country, longitude, latitude) |>
  summarise(channel_count = n())

world_map <- leaflet() |>
  addTiles() |>
  addMarkers(
    data = channel_counts_by_location,
    ~longitude, ~latitude,
    label = ~paste(country, ": ", channel_count, " channels"),
    popup = TRUE
  )

world_map
```

We find that the top five ranked YouTubers are from the United States (N = 311), followed by India (N = 168), Brazil (N = 61), the United Kingdom (N = 43), and Mexico (N = 33).

#### Most Popular YouTube Content Categories by Country
```{r}
cleaned_youtube_df <- cleaned_df %>%
                      filter(created_year >= 2005, !is.na(category), category != "nan")


world <- map_data("world")

world <- world %>%
          mutate(region = ifelse(region == "USA", "United States", region),
                 region = ifelse(region == "UK", "United Kingdom", region))


popular_category <- cleaned_youtube_df %>%
                    group_by(country) %>%
                    summarise(most_popular_category = names(sort(table(category), decreasing = TRUE)[1])) %>%
                    ungroup()

world.plus1 <- world %>% 
               left_join(popular_category, by = c("region" = "country")) %>%
               filter(region != "Antarctica")

world.plus1$most_popular_category[is.na(world.plus1$most_popular_category)] <- "Unknown"

categories <- unique(world.plus1$most_popular_category)

color <- c("#ffd180","#ffa07a","#d1d17a", "#8dab7f", "#D2DFD9", "#A8C0B5", "#D1B9CB", "#B3CDD1", "#BBC1D0", "#E8C3C3","#C7CEBD", "#D2DFD9","#6b8e23")


category_colors <- setNames(color, categories)

ggplot(data = world.plus1, mapping = aes(x = long, y = lat, group = group)) + 
    coord_fixed(1.3) +
    geom_polygon(aes(fill = most_popular_category)) +
    ggtitle("Most Popular YouTube Content Categories by Country") +
    scale_fill_manual(values = category_colors) +
    theme_minimal() +
    theme(
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      plot.title = element_text(hjust = 0.5),
      legend.title = element_blank(),
      legend.position = "bottom"
    )
```

YouTube content preferences vary widely by country, reflecting cultural diversity in digital consumption. Music, People & Blogs are the most popular genres across world. The presence of an "Unknown" category could indicate data gaps or emerging genres yet to be classified. The map underscores the importance of cultural context in content creation and consumption on YouTube.


#### How are the numeric variables correlated?

```{r fig.width = 9,fig.asp = 0.8}
# Calculate the correlation matrix
cor_matrix <- cor(youtube_df[, columns_to_plot], use = "complete.obs")

fig <- plot_ly(x = colnames(cor_matrix), y = rownames(cor_matrix), z = cor_matrix, 
               type = "heatmap",colorscale ="Greens"  , zmin = -1, zmax = 1)

fig <- fig %>% layout(
  yaxis = list(autorange = "reversed"),
  width=800,
  height=600,
  title = "Correlation Matrix")

fig
```

The correlation coefficient values range from -1 to 1, where 1 indicates a perfect positive correlation, -1 indicates a perfect negative correlation, and 0 indicates no correlation. The heatmap indicates strong positive correlations between `subscribers` and `video views`, as well as among various earnings metrics, suggesting that higher subscriber counts are associated with more views and consistent earnings patterns. Other variables like `video_per_upload` show moderate correlations with recent engagement metrics, while `earning_differences` exhibit a lower correlation with viewership-related variables, hinting at additional factors influencing earnings beyond just subscriber and view counts.

#### Bubble Chart: Subscribers vs. Video Views by Category

```{r fig.width = 9}

size_factor <- 10^(-8.7) # Adjust this factor as needed to scale sizes up or down

youtube_df %>%
  filter(!is.na(category) & category != "nan") %>%
  plot_ly(
    x = ~subscribers, 
    y = ~video_views, 
    size = ~video_views_for_the_last_30_days * size_factor, 
    color = ~category,
    text = ~category,
    hoverinfo = 'text+x+y',
    type = 'scatter',
    mode = 'markers',
    marker = list(
      sizemode = 'area',
      sizeref = 2 * max(youtube_df$video_views_for_the_last_30_days * size_factor)/100
    )
  ) %>%
  layout(
    title = 'Subscribers vs. Video Views by Category',
    xaxis = list(type = 'log', title = 'Subscribers'),
    yaxis = list(type = 'log', title = 'Video Views (in billions)'),
    hovermode = 'closest',
    showlegend = TRUE
  )
```

The bubble chart implies the relationship between the number of subscribers (on the x-axis) and video views (on the y-axis) for YouTube channels: more subscribers tend to have a higher number of total video views. The size of the bubbles represent the video views in the last 30 days, and color hue represents the category. Certain categories like Music, Entertainment, and Gaming appear more frequently among the channels with higher views and subscribers, reflecting their popularity on Youtube.


#### Relationship between Views per Upload and Highest Yearly Earning

```{r}
perUploadData <- cleaned_df |>
  mutate(viewsPerUpload = video_views / uploads) |>
  filter(viewsPerUpload < 600000000)

scatter_plot_perUpLoad <- ggplot(data = perUploadData, aes(x = viewsPerUpload, y = highest_yearly_earnings)) +
  geom_point(alpha=0.7,color="#8dab7f") +
  geom_smooth(method = "lm", color = "#ffa07a") + 
  labs(title = 'Scatter Plot of Highest Yearly Earnings vs. Views per Upload for Content Creators',
       x = 'Views per Upload',
       y = 'Highest Yearly Earnings')+
  theme_minimal()

# Print the plot
print(scatter_plot_perUpLoad)
```

The scatterplot illustrates a discernible but weak downward slope between the highest earning and the number of YouTube views per upload. This implies that, in general, channels with a higher number of views per upload tend to have slightly lower earnings. While the relationship is present, its strength is limited, indicating that other factors beyond views per upload are likely influencing the earnings of YouTube channels.

## Model Fitting

We explored three variables to measure a YouTuber's success: Subscribers, Earnings Differences, and Highest Yearly Earnings. Across these three models, we consistently applied the same predictors: `country`, `category`, `video_per_upload`, `uploads`, `video_views` are applied.

#### 1. Fit the multiple linear regression model of **_subscribers_**
Model statement:
$subscribers =\beta_0+ \beta_1country +\beta_2category +\beta_3videoperupload + \beta_4uploads + \beta_5videoviews$

```{r}
youtube_df <- youtube_df %>% drop_na()
# Fit the Multiple Linear Regression model++uploads +video_views, data = youtube_df)
mlr_model <- lm(subscribers ~ country + category + video_per_upload +uploads +video_views , data = youtube_df)
  
youtube_df %>% 
  modelr::add_predictions(mlr_model) %>% 
  ggplot(aes(x = earning_differences, y = pred)) +
  geom_point() +
  labs(
        title = "Multivariate Linear Model",
        x = "earning_differences",
        y = "subscribers") +
  theme_pubclean()

check_model(mlr_model, check = c("linearity", "outliers", "qq", "normality"))

# Summary of the model
mlr_model%>% 
broom::tidy()%>% 
knitr::kable(digits=3) 

mlr_model %>% 
broom::glance() %>%
knitr::kable(digits=3)
```

#### Interpretation for model 1

1. **Residuals**:
   Large values for the minimum and maximum suggest the presence of outliers.

2. **Coefficients**:
   Most of the country and category levels are not statistically significant predictors of subscribers (p > 0.05), except for 'countrySouth Korea' which is significant (p = 0.0126). 'video_per_upload' is not a significant predictor, while 'uploads' is significant. The variable 'video_views' is highly significant (p < 2e-16), indicating a strong association with the number of subscribers.

3. **Model Summary**:
   The high Multiple R-squared value of 75.26% indicates that a significant proportion of the variability in subscriber counts can be explained by the independent variables included in the model, demonstrating its strong predictive power. The Adjusted R-squared value of 72.4% reaffirms this, suggesting that the model is appropriately balanced with the right number of predictors. The F-statistic confirms the model's overall statistical significance.
   

#### 2. Fit the multiple linear regression model of **_earning_differences_**

Model statement:
$earningdifferences =\beta_0+ \beta_1country +\beta_2category +\beta_3videoperupload + \beta_4uploads + \beta_5videoviews$

```{r}
mlr_model_1 <- lm(earning_differences ~ country + category + video_per_upload +uploads +video_views , data = youtube_df)
  
  youtube_df %>% 
  modelr::add_predictions(mlr_model_1) %>% 
  ggplot(aes(x = earning_differences, y = pred)) +
  geom_point() +
  labs(
        title = "Multivariate Linear Model",
        x = "earning_differences",
        y = "predictions") +
  theme_pubclean()

check_model(mlr_model_1, check = c("linearity", "outliers", "qq", "normality"))

# Summary of the model
mlr_model_1%>% 
broom::tidy() %>%
knitr::kable(digits=3)

mlr_model_1 %>% 
broom::glance() %>%
knitr::kable(digits=3)
```

#### interpretation for model2

1. **Residuals**:
   Large residuals imply potential outliers or limitations in the model's ability to capture data patterns effectively.

2. **Coefficients**:
   Most of the country and category coefficients are not statistically significant (p > 0.05) except for 'countrySouth Korea'. 'video_per_upload' also lacks statistical significance (p = 0.3893). 'video_views' is highly significant (p < 2e-16), indicating a strong association with 'earning_differences'.

3. **Model Summary**:
   The Multiple R-squared value, at 43.86%, denotes the proportion of variance in 'earning_differences' explained by the independent variables. The Adjusted R-squared, at 37.36%, accounts for predictor count and provides a more precise measure of model fit. The F-statistic's low associated p-value underscores the overall statistical significance of the model.


#### 3. Fit the multiple linear regression model of **_highest_yearly_earnings_**

Model statement:
$highestyearlyearnings =\beta_0+ \beta_1country +\beta_2category +\beta_3videoperupload + \beta_4uploads + \beta_5videoviews$

```{r}
mlr_model_2 <- lm(highest_yearly_earnings ~ country + category + video_per_upload+uploads +video_views , data = youtube_df)

  youtube_df %>% 
  modelr::add_predictions(mlr_model_2) %>% 
  ggplot(aes(x = earning_differences, y = pred)) +
  geom_point() +
  labs(
        title = "Multivariate Linear Model",
        x = "highest_yearly_earnings",
        y = "predictions") +
  theme_pubclean()

check_model(mlr_model_2, check = c("linearity", "outliers", "qq", "normality"))

# Summary of the model
mlr_model_2%>% 
broom::tidy() %>%
knitr::kable(digits=3)

mlr_model_2 %>% 
broom::glance() %>%
knitr::kable(digits=3)
```

#### interpretation for model 3


1. **Residuals**:
   The large range suggests the presence of outliers or extreme values in the data.

2. **Coefficients**:
   Most of the country and category coefficients are not statistically significant (p > 0.05) except for 'countrySouth Korea','countryLatvia'. 'video_per_upload' is not a significant predictor (p = 0.29118).'video_views' has a positive and highly significant coefficient (p < 2e-16), indicating a strong and statistically significant relationship with 'highest_yearly_earnings'.
   
3. **Model Summary**:
   The Multiple R-squared value, at 43.87%, denotes the proportion of variance in 'highest_yearly_earnings' explained by the independent variables. The Adjusted R-squared, at 37.37%, accounts for predictor count and provides a more precise measure of model fit. The F-statistic's low associated p-value underscores the overall statistical significance of the model.
   
#### Discussion for three linear models

In summary, Models 2 and 3, which predict 'earning_differences' and 'highest_yearly_earnings' respectively, share similar results may because they both involve financial aspects of a YouTuber's success. 'video_views' consistently emerges as a strong predictor of success across all three models. While country and category variables do not consistently impact success, a few countries (South Korea and Latvia) exhibit unique effects. These models collectively provide valuable insights into the factors influencing YouTuber success. The respective $r^2$ of three models are $0.754, 0.438, 0.438$. A high $r^2$ indicates a better model fit. This suggests that the number of subscribers may be a more appropriate metric to quantify the success of YouTube creators.

#### 4. Fit the Random Forest Regression model of **_subscribers_**
To Proceed our project, we further develop a random forest model to predict the number of subscribers, expecting for a higher $r^2$. The data was split into training data and test data with a proportion of 0.8. 

```{r}
library(randomForest)
library(caTools)
set.seed(42) # for reproducibility
split <- sample.split(youtube_df$subscribers, SplitRatio = 0.8)
train_data <- subset(youtube_df, split == TRUE)
test_data <- subset(youtube_df, split == FALSE)

# Train a Random Forest model
rf_modelS <- randomForest(subscribers ~ ., data=youtube_df, importance=TRUE)

# Make predictions on the test set
predictions <- predict(rf_modelS, test_data)

# Calculate R^2 score
r2_score <- cor(test_data$subscribers, predictions)^2

# Output the model and R^2 score
print(rf_modelS)
print(r2_score)
```

#### interpretation for random forest

The Random Forest Regression model with 500 trees and 6 variables considered at each split explains about 85.25% of the variance in the number of subscribers, indicating a strong predictive performance with relatively low mean squared residuals. Additionally, the 
$r^2$ for testing is approximately 0.981, signifying a high level of accuracy in predicting subscribers. This suggests that the Random Forest model explains almost all the variability in the subscriber count. 

## Discussion
We also check the linear regression assumptions (e.g., homoscedasticity, normality of residuals) and observe potential outliers that can impact the model's accuracy. To enhance model accuracy, we may consider removing these outliers and subsequently explore missing value imputation. In summary, the Random Forest model proves highly effective for this dataset; however, further validation, potentially with different datasets or cross-validation, is advisable to ensure the model's generalizability and assess the potential impact of overfitting.










