---
title: "Data Visualization"
output: 
  html_document:
    toc: true
---

Load necessary packages.
```{r}
library(tidyverse)
library(plotly)
library(ggplot2)
library(scales)
library(reshape2)
library(ggwordcloud)
library(stringi)
```

Read the dataset and drop `NA` vlaues.
```{r}
youtube_df <- read_csv("Data/cleaned_youtube_df.csv") %>% 
  janitor::clean_names() %>% 
  filter(created_year >= 2005) %>% 
  drop_na()
```

```{r}
summary(youtube_df)
```

We use histogram and density plot to intuitively visualize the distribution of different variables.
```{r fig.width = 9,fig.asp = 1.2,out.width = "100%"}

all_columns <- colnames(youtube_df)
columns_to_plot <- all_columns[!all_columns %in% c("id", "category","country","abbreviation","channel_type","population","latitude","longitude","created_year")]


numeric_data_long <- 
  youtube_df[, columns_to_plot] %>% 
  gather(key = "variable", value = "value")


# Create a single plot with facets for each numeric variable
p <- ggplot(numeric_data_long, aes(x = value)) +
  geom_histogram(aes(y = ..density..),bins = 15, fill = "#8dab7f", alpha = 0.8) +
  geom_density(color="#6b8e23")+
  facet_wrap(~ variable, scales = "free", ncol = 3) +
  scale_x_continuous(labels = scales::comma) +
  theme_minimal(base_size = 10) +  
  theme(
    strip.text.x = element_text(size = 10, face = "bold"), 
    axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1,size=7,face = "bold"), # Angle x-axis labels for readability
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    plot.margin = margin(1, 1, 1, 1, "cm"), # Adjust the plot margins
    strip.background = element_blank(),
    panel.spacing = unit(3, "lines")
  ) +
  labs(
    title = "Distribution of Numeric Variables",
    x = "Value",
    y = "Frequency",
    caption = "Source: YouTube Data"
  )
# Convert to an interactive plot
ggplotly(p)
```

We plot heatmap to study the relationships among numerical variables.
```{r fig.width = 9,fig.asp = 0.8}


# Calculate the correlation matrix
cor_matrix <- cor(youtube_df[, columns_to_plot], use = "complete.obs")

fig <- plot_ly(x = colnames(cor_matrix), y = rownames(cor_matrix), z = cor_matrix, 
               type = "heatmap",colorscale ="Greens"  , zmin = -1, zmax = 1)

fig <- fig %>% layout(
  yaxis = list(autorange = "reversed"),
  width=800,
  height=600,
  title = "Correlation Matrix")

fig
```

Wordcloud for channel category.

```{r}
category_data <- youtube_df %>%
  filter(!is.na(category) & category != "nan") %>%
  count(category) %>%
  mutate(n=n*30) %>% 
  ungroup()


category_data$scaled_size <- log(category_data$n + 1) # adding 1 to avoid log(0)

wordcloud_plot <- ggplot(category_data, aes(label = category, size = scaled_size)) +
  geom_text_wordcloud(
    aes(color = n),
    shape = 'circle',
    rm_outside = TRUE
  ) +
  scale_size_area(max_size = 10) + 
  scale_color_gradient(low = "#ffcc99", high = "#8dab7f") +
  theme_void(base_family = "sans") +
  theme(legend.position = "none", 
        plot.margin = margin(1, 1, 1, 1, "cm")) # Adjust margins around the plot

# Display the plot
wordcloud_plot


```

Pie chart for channel type.
```{r fig.width = 3,fig.asp = 1.5,out.width = "100%"}
channel_type_counts <- table(youtube_df$channel_type)

channel_type_counts <- youtube_df %>%
  group_by(channel_type) %>%
  summarise(count = n()) %>%
  ungroup()

color <- c("#ffcc99","#ffe4b5", "#ffd180","#ffa07a","#d1d17a", "#8dab7f", "#D2DFD9", "#A8C0B5", "#D1B9CB", "#B3CDD1", "#BBC1D0", "#E8C3C3","#C7CEBD", "#D2DFD9","#6b8e23")

# Create a pie chart using plotly with the custom colors
fig <- plot_ly(channel_type_counts, labels = ~channel_type, values = ~count, type = 'pie',
               textinfo = 'label+percent',
               insidetextorientation = 'radial',
               marker = list(colors = color))
fig %>% 
  layout(title = 'Pie Chart of Channel Types',
         showlegend = FALSE,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

```
Bubble Chart: Subscribers vs. Video Views by Category
```{r fig.width = 9}

size_factor <- 10^(-8.7) # Adjust this factor as needed to scale sizes up or down

youtube_df %>%
  filter(!is.na(category) & category != "nan") %>%
  plot_ly(
    x = ~subscribers, 
    y = ~video_views, 
    size = ~video_views_for_the_last_30_days * size_factor, 
    color = ~category,
    text = ~category,
    hoverinfo = 'text+x+y',
    type = 'scatter',
    mode = 'markers',
    marker = list(
      sizemode = 'area',
      sizeref = 2 * max(youtube_df$video_views_for_the_last_30_days * size_factor)/100
    )
  ) %>%
  layout(
    title = 'Subscribers vs. Video Views by Category',
    xaxis = list(type = 'log', title = 'Subscribers'),
    yaxis = list(type = 'log', title = 'Video Views (in billions)'),
    hovermode = 'closest',
    showlegend = TRUE
  )
```

Here I want to investigate the top 10 YouTube channels by the highest yearly earnings. I'll load the original dataset again.

```{r}
color <- c("#ffe4b5", "#ffa07a","#d1d17a" , "#D2DFD9", "#A8C0B5", "#D1B9CB", "#B3CDD1", "#BBC1D0", "#E8C3C3")
earning_plot_data <-
  read_csv("Data/Global YouTube Statistics.csv",locale = locale(encoding = "Windows-1252"))  %>% 
  janitor::clean_names() %>% 
  drop_na() %>% 
  select(youtuber, channel_type, highest_yearly_earnings) %>% 
  mutate(youtuber = stringi::stri_replace_all_regex(youtuber, "[^\x01-\x7F]", "")) %>% 
  arrange(desc(highest_yearly_earnings)) %>%
  top_n(15, highest_yearly_earnings)



plot_ly(earning_plot_data, x = ~highest_yearly_earnings, y = ~youtuber, 
                type = 'bar', orientation = 'h',
                color = ~channel_type, colors = color,
                text = ~paste('$', formatC(highest_yearly_earnings, format = "d", big.mark = ",")),
                textposition = 'inside',
                insidetextanchor = 'end', 
                textfont = list(color = 'white'), # text color
                hoverinfo = 'text',
                hovertemplate = paste('<b>Youtuber:</b> %{y}<br>',
                                      '<b>Earnings:</b> $%{x}<extra></extra>')) %>%
  layout(title = 'Top 15 YouTube Channels by Highest Yearly Earnings',
         xaxis = list(title = 'Yearly Earnings ($)'),
         yaxis = list(title = ''),
         showlegend = TRUE,
         margin = list(l = 100, r = 25, t = 50, b = 50),
         font = list(family = "Arial, sans-serif", size = 12, color = "#333333"))




```

